\textbf{NAME OF THIS STUDY}

### 2018-11-06 submission/manuscript.Rmd
playing with tables

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
# Load useful functions
source('../code/learning/functions.R')
# Read in necessary libraries
deps = c("doParallel","pROC", "caret","knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t')
kable(model_param, caption = "Table 1 Parameters and software implementation of the classification algorithms")
```
\vspace{35mm}

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
# Load useful functions
source('../code/learning/functions.R')
# Read in necessary libraries
deps = c("kableExtra", "kable","doParallel","pROC", "caret","knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t')
kable(model_param, caption = "Table 1 Parameters and software implementation of the classification algorithms") %>%
  kable_styling("striped", full_width = F)
```
\vspace{35mm}

### 2018-11-06 submission/manuscript.tex
playing with tables

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={NAME OF THIS STUDY},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={NAME OF THIS STUDY},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{longtable}[]{@{}lllllrl@{}}
\caption{Table 1 Parameters and software implementation of the
classification algorithms}\tabularnewline
\toprule
Method & Parameter & Value & Cross.Validation & Scaler & Epochs &
Sofware.Implementation\tabularnewline
\midrule
\endfirsthead
\toprule
Method & Parameter & Value & Cross.Validation & Scaler & Epochs &
Sofware.Implementation\tabularnewline
\midrule
\endhead
Logistic Regression & C & {[}0.01, 0.1, 1, 10{]} & 5-fold 100 repeats &
MinMaxScaler & 100 & Sklearn-LogisticRegression\tabularnewline
L1 SVM Linear Kernel & C & {[}0.001, 0.01, 0.1 ,1{]} & 5-fold 100
repeats & StandardScaler & 100 & Sklearn-LinearSVC\tabularnewline
L2 SVM Linear Kernel & C & {[}0.01, 0.1, 1{]} & 5-fold 100 repeats &
StandardScaler & 100 & Sklearn-LinearSVC\tabularnewline
SVM RBF Kernel & C, gamma & {[}0.000001, 0.00001, 0.0001, 0.001,
0.01{]}, {[}0.000000001, 0.00000001, 0.0000001{]} & 5-fold 100 repeats &
StandardScaler & 100 & Sklearn-SVC\tabularnewline
Decision Tree & max\_depth, min\_samples\_split & {[}6, 8, 10, 50{]},
{[}10, 25, 50{]} & 5-fold 100 repeats & MinMaxScaler & 100 &
DecisionTreeClassifier\tabularnewline
Random Forest & n\_estimators, max\_features & 1000, {[}10, 80, 500,
1000, 1500{]} & 5-fold 100 repeats & MinMaxScaler & 100 &
RandomForestClassifier\tabularnewline
XGBoost & n\_estimators, colsample\_bytree, learning\_rate, subsample,
max\_depth, min\_child\_weight & 100, 0.8, {[}0.01, 0.1, 1{]},
{[}0.7,0.8,0.9{]}, {[}6,7,8{]}, {[}1,2,3{]} & 5-fold 100 repeats &
MinMaxScaler & 100 & XGBClassifier\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\raggedright\strut
\vspace{35mm}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright\strut
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
